---
title: "UWBiost561 Demo"
author: "Seth Peacock"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
vignette: >
  %\VignetteIndexEntry{Demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette provides an example for the three main functions of this package: namely, `generate_partial_clique`, `compute_maximal_partial_clique`, and `execute_simulation`. First, we load the package and set the seed.

```{r}
library(UWBiost561)
set.seed(3910458)
```


### `generate_partial_clique`
This function randomly generates an adjacency matrix and is the used in the `execute_simulation` function. 
```{r}
adj_matrix <- generate_partial_clique(n=8,
                                      clique_fraction=0.5,
                                      clique_edge_density=0.7)
adj_matrix
```

### `compute_maximal_clique`
Provided an adjacency matrix, the `compute_maximal_clique` function returns the indices of a partial clique with the required density, `alpha`, along with other information. The partial clique may not be the true maximal clique as it does not conduct an exhaustive search.
```{r}
compute_maximal_partial_clique8(adj_mat=adj_matrix$adj_matrix,
                               alpha=.7)
```

### `execute_simulation`
This function test each `compute_maximal_cliqueN` on matrices of the given levels. It returns a data frame with the size of the partial clique returned by each function, if the clique was valid, and the time it took to run.

```{r}
execute_simulation(trials_per_level=2,
                   n_nodes=c(5),
                   clique_fraction=c(0.5),
                   alpha=c(1))
```

